Classless Java: Tuning Java Interfaces

### 2015-11-25 paper/sections/CaseStudy.tex
game case study revised. run.sh script should be working on your machines.

\subsection{A Maze Game}
The last case study is a simple Maze game, which is used\bruno{where?}
to evaluate code reuse ability related to inheritance and design
patterns. In the game, there is a player with the goal of collecting
as many coins as possible. She may enter a room with several doors to
be chosen among. This is a good example because it involves code reuse
(different kinds of doors inherit a common type, with different
features and behaviour), multiple inheritance (a special kind of door
may require features from two other door types) and it also shows how
to model operations \texttt{symmetric sum}, \texttt{override} and
\texttt{alias} as trait-oriented programming. The game has been
implemented using plain Java 8 and default methods by Bono
et. al~\cite{bono14}, and the code for that implementation is
available online. We reimplemented the game using \mixin. Due to space
constraints, we omit the code here. The following table summarizes
the number of lines of code and classes/interfaces in each implementation:

@@

\noindent The \mixin annotation allowed us to reduce the interfaces/classes used
in Bono et al.'s implementation by 21.4\% (from 14 to 11). The
reductions was due to the replacement of instantiation classes with
generated \texttt{of} methods. The number of source lines of code (SLOC)
was reduced by 40\%\bruno{explain why? we generate code for getters/setters?}. 
To ensure a fair comparison, we used the same coding style as Bono et al.'s.

>>>>

\subsection{A Small Game Example}
The last case study is a simple Maze game, which is often
used~\cite{gof,bono14,vicentedesign} 
\bruno{where?}
\yanlin{the last one ``design patterns in OCaml''is not a proper paper, not sure
whether to cite.}
to evaluate code reuse ability related to inheritance and design
patterns. In the game, there is a player with the goal of collecting
as many coins as possible. She may enter a room with several doors to
be chosen among. This is a good example because it involves code reuse
(different kinds of doors inherit a common type, with different
features and behaviour), multiple inheritance (a special kind of door
may require features from two other door types) and it also shows how
to model operations \texttt{symmetric sum}, \texttt{override} and
\texttt{alias} as trait-oriented programming. The game has been
implemented using plain Java 8 and default methods by Bono
et. al~\cite{bono14}, and the code for that implementation is
available online. We reimplemented the game using \mixin. Due to space
constraints, we omit the code here. The following table summarizes
the number of lines of code and classes/interfaces in each implementation:

@@

\noindent The \mixin annotation allowed us to reduce the interfaces/classes used
in Bono et al.'s implementation by 21.4\% (from 14 to 11). The
reductions was due to the replacement of instantiation classes with
generated \texttt{of} methods. The number of source lines of code (SLOC)
was reduced by 40\% due to both the removal of instantiation overhead and
generation of getters/setters. %\bruno{explain why? we generate code for getters/setters?}. 
To ensure a fair comparison, we used the same coding style as Bono et al.'s.
